\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-09 main.tex

\begin{code}
\begin{minted}[fontsize=\small]{python}
# Create a device representing square thin film.
device = sc.Device(
    "film",
    layers=[sc.Layer("base", Lambda=0, z0=0)],
    films=[sc.Polygon("film", layer="base", points=sc.geometry.square(20))],
    # Add an abstract_polygon near the vortex position so that
    # that region will be meshed densely.
    abstract_regions=[
        sc.Polygon("circle", layer="base", points=sc.geometry.circle(0.1)),
    ],
    length_units="um",
)
device.make_mesh(min_triangles=8000)
# Specify the vortex position.
vortices = [sc.Vortex(x=0, y=0, layer="base")]
# Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
Lambdas = np.linspace(0, 1, 6) # [device.length_units]
solutions = []
for Lambda in Lambdas:
    device.layers["base"].Lambda = Lambda
    solution = sc.solve(
        device=device, vortices=vortices, field_units="Phi_0/um**2"
    )[-1]
    solutions.append(solution)
\end{minted}
\captionof{listing}{}
\label{code:pearl-vortex}
\end{code}

>>>>

\begin{code}
\begin{minted}[fontsize=\small]{python}
# Create a device representing square thin film.
device = sc.Device(
    "film",
    layers=[sc.Layer("base", Lambda=0, z0=0)],
    films=[sc.Polygon("film", layer="base", points=sc.geometry.square(20))],
    # Add an abstract_polygon near the vortex position so that
    # that region will be meshed densely.
    abstract_regions=[
        sc.Polygon("circle", layer="base", points=sc.geometry.circle(0.1)),
    ],
    length_units="um",
)
device.make_mesh(min_triangles=8000)
# Specify the vortex position.
vortices = [sc.Vortex(x=0, y=0, layer="base")]
# Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
Lambdas = np.linspace(0, 1, 6) # [device.length_units]
solutions = []
for Lambda in Lambdas:
    device.layers["base"].Lambda = Lambda
    solution = sc.solve(
        device=device, vortices=vortices, field_units="Phi_0/um**2"
    )[-1]
    solutions.append(solution)
    # Use solution.field_at_position() to evaluate the magnetic field profile.
\end{minted}
\captionof{listing}{}
\label{code:pearl-vortex}
\end{code}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
    \caption{Caption}
    \label{fig:pearl}
\end{figure}
